Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-09 volunteer-clouds-ieee-ci-si.tex
una letra d se había quedado suelta en la página 5, junto a la TABLE I (la he quitado)
una falta de ortografía en la línea 706 del .tex (arreglada)

Initial experiments were set up using the OpenShift
PaaS, which provides a free tier within which this %Ya se defnió antes PaaS
experiment could be performed. That way, and as required, the hardware
and cloud cost for this experiment were zero. Experiments were
announced through a post in Twitter and other social networks, and
results were published here \cite{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the months of April and then by the beginning of August. All
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 40-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions reset to the void set. No special care was taken to wait
until all clients had finished, thus it might happen that, in fact,
the islands running in the browser {\em spill} from one experiment to
the next. However, previous experiments have proven that the influence
of these islands in the next experiment is, in fact negligible.
%
\begin{table*}d
\caption{Characteristics of the volunteer computing initial runs. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rr}
\hline
Date & \# experiments & Different IPs \\
\hline
April 4th 4/4 & 57 & 191 \\
April 24th 4/24 &  231 & 559 \\
July 31th 7/31 & 97 & 179 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{table*}
\caption{Summary of time per run, number of IPS and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|ccccccc}
\hline
Date & Median \#IPs & Max \#IPs & Median time (s) & Median \#{\tt
  PUT}s & $<$ 69s & $<$ 3.46s & Inter-experiment correlation\\
\hline
4/4 & 5 & 16 & 2040 & 18 & 14.29\% & 5.36\% & 0.0082 \\
4/24 &  5 & 29 & 732 & 11 & 47.39\% & 3.91\% & 0.0934\\
7/31 & 5 & 14 & 260 & 23 & 27.08\% & 1.04\%  & 0.1741\\
\hline
\end{tabular}
\end{center}
\end{table*}
%
The table shows that every run included more than 50 experiments. The %FERGU: No debería ser mejor al revés? Cada experimento está compuesto de varias runs. De todas maneras arriba lo has definido así, así que si no quieres no lo cambies. Pero me parece más correcto que un experimento tenga runs, en vez de al revés
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment.

@@

It is interesting also to check the distribution of the experiment
duration, shown in Figure \ref{fig:zipf:os} and which roughly follows
a Zipf's law, with similar distribution along all three runs. The 4/24
run is the most complete and shows a S-shape, which implies an
accumulation of experiments taking similar time and around 100
seconds. The most interesting part is the {\em tail}, which shows how
many experiments took a desirable amount of time, and of the order of
10 seconds. As it can be seen, it drops sharply implying there are
just a few of them, and with diminishing probability as time
decreases. This exponential distribution also appears in the
distribution of HTTP {\tt PUT}s, equivalent to the number of
generations divided by 100, contributed by every user, which is shown
in Figure \ref{fig:puts:os}. These results show a Zipf-like behavior,
so we have fitted it to the Generalized Extreme Value distribution,
with the resulting parameters shown in Table \ref{tab:puts:os}.
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value distribution of
  the number of {\tt PUT}s per unique IP. \label{tab:puts:os}}
\begin{center}
\begin{tabular}{l|ccc}
\hline
Date  & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
4/4 &  8.541 $\pm$ 1.0926  &    12.442 $\pm$ 1.7302 &  1.388 $\pm$
0.1377 \\
4/24 & 6.148 $\pm$ 0.3782 & 7.354 $\pm$ 0.5105 & 1.090 $\pm$  0.0697  \\
7/31 & 11.645 $\pm$ 1.475 & 16.365 $\pm$ 2.201 &  1.265 $\pm$ 0.132   \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
This distribution was originally proposed to fit extreme values
\cite{resnick2013extreme} and contains, as a special case, the inverse
Weibull distribution which was fitted to volunteer computing
frameworks such as SETI@home \cite{javadi2009mining}. This
distribution is governed by three parameters, the usual location $\mu$
which is related to where it has its {\em center} and  scale $\sigma$,
related to the size, but also a third shape $\xi$ parameter that is
related to its skewness, that is, how skewed it is around the central
location. Positive parameters indicate that the distribution {\em
  leans} towards the origin, negative towards the other extreme
value. In this case, Table \ref{tab:puts:os} shows $\xi$ values
greater than one and between one and 1.4, which indicates that the
three experiment share this origin-leaning pattern, with many users
donating a few cycles and just a few donating extreme values. Random
distributions with these parameters have been plotted in red in
\ref{fig:puts:os}, indicating that the fit is good enough. The
predictive value of these fits, however, is limited, over all taking
into account the low correlation between successive events shown
above.

>>>>

Initial experiments were set up using the OpenShift
PaaS, which provides a free tier within which this %Ya se defnió antes PaaS
experiment could be performed. That way, and as required, the hardware
and cloud cost for this experiment were zero. Experiments were
announced through a post in Twitter and other social networks, and
results were published here \cite{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the months of April and then by the beginning of August. All
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 40-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions reset to the void set. No special care was taken to wait
until all clients had finished, thus it might happen that, in fact,
the islands running in the browser {\em spill} from one experiment to
the next. However, previous experiments have proven that the influence
of these islands in the next experiment is, in fact negligible.
%
\begin{table*}
\caption{Characteristics of the volunteer computing initial runs. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rr}
\hline
Date & \# experiments & Different IPs \\
\hline
April 4th 4/4 & 57 & 191 \\
April 24th 4/24 &  231 & 559 \\
July 31th 7/31 & 97 & 179 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{table*}
\caption{Summary of time per run, number of IPS and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|ccccccc}
\hline
Date & Median \#IPs & Max \#IPs & Median time (s) & Median \#{\tt
  PUT}s & $<$ 69s & $<$ 3.46s & Inter-experiment correlation\\
\hline
4/4 & 5 & 16 & 2040 & 18 & 14.29\% & 5.36\% & 0.0082 \\
4/24 &  5 & 29 & 732 & 11 & 47.39\% & 3.91\% & 0.0934\\
7/31 & 5 & 14 & 260 & 23 & 27.08\% & 1.04\%  & 0.1741\\
\hline
\end{tabular}
\end{center}
\end{table*}
%
The table shows that every run included more than 50 experiments. The %FERGU: No debería ser mejor al revés? Cada experimento está compuesto de varias runs. De todas maneras arriba lo has definido así, así que si no quieres no lo cambies. Pero me parece más correcto que un experimento tenga runs, en vez de al revés
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment.

@@

It is interesting also to check the distribution of the experiment
duration, shown in Figure \ref{fig:zipf:os} and which roughly follows
a Zipf's law, with similar distribution along all three runs. The 4/24
run is the most complete and shows a S-shape, which implies an
accumulation of experiments taking similar time and around 100
seconds. The most interesting part is the {\em tail}, which shows how
many experiments took a desirable amount of time, and of the order of
10 seconds. As it can be seen, it drops sharply implying there are
just a few of them, and with diminishing probability as time
decreases. This exponential distribution also appears in the
distribution of HTTP {\tt PUT}s, equivalent to the number of
generations divided by 100, contributed by every user, which is shown
in Figure \ref{fig:puts:os}. These results show a Zipf-like behavior,
so we have fitted it to the Generalized Extreme Value distribution,
with the resulting parameters shown in Table \ref{tab:puts:os}.
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value distribution of
  the number of {\tt PUT}s per unique IP. \label{tab:puts:os}}
\begin{center}
\begin{tabular}{l|ccc}
\hline
Date  & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
4/4 &  8.541 $\pm$ 1.0926  &    12.442 $\pm$ 1.7302 &  1.388 $\pm$
0.1377 \\
4/24 & 6.148 $\pm$ 0.3782 & 7.354 $\pm$ 0.5105 & 1.090 $\pm$  0.0697  \\
7/31 & 11.645 $\pm$ 1.475 & 16.365 $\pm$ 2.201 &  1.265 $\pm$ 0.132   \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
This distribution was originally proposed to fit extreme values
\cite{resnick2013extreme} and contains, as a special case, the inverse
Weibull distribution which was fitted to volunteer computing
frameworks such as SETI@home \cite{javadi2009mining}. This
distribution is governed by three parameters, the usual location $\mu$
which is related to where it has its {\em center} and  scale $\sigma$,
related to the size, but also a third shape $\xi$ parameter that is
related to its skewness, that is, how skewed it is around the central
location. Positive parameters indicate that the distribution {\em
  leans} towards the origin, negative towards the other extreme
value. In this case, Table \ref{tab:puts:os} shows $\xi$ values
greater than one and between one and 1.4, which indicates that the
three experiments share this origin-leaning pattern, with many users
donating a few cycles and just a few donating extreme values. Random
distributions with these parameters have been plotted in red in
\ref{fig:puts:os}, indicating that the fit is good enough. The
predictive value of these fits, however, is limited, over all taking
into account the low correlation between successive events shown
above.
